---
title: "hello world"
description: |
  I've started a blog to teach myself Quarto and explore, experiment, and find excitement in data science and statistics.
date: "2021-04-05"
categories: [blogging, learning]
#image:
#image-alt: 
#citation:
#  url: 
---

<!--------------- my typical setup ----------------->

```{r setup, include=FALSE}
long_slug <- "2024-04-20_helloworld"
```


<!--------------- post begins here ----------------->

hi! welcome to my blog!

I've been working in (practicing?) R for the last 5 years and
thought starting a Quarto based blog would be a great way to both continue to 
learn and be a more active participant in the community that has taught (and continues to!) me so much.

Back in the MySpace and Xanga days I enjoyed dipping my toe in the HTML pool 
and with R Markdown and now Quarto I've started exploring the wonderful worlds 
of YAML, CSS, and even Makefiles.

It was just today that I discovered Danielle Navarro's 
[blog](https://blog.djnavarro.net) and this absolutely shamelessly has been 
built upon hers with great reverence and equally as much inspiration from 
[Jenny Bryan](https://jennybryan.org/about/), [Julia Silge](https://juliasilge.com/blog/), 
and most of all the incredible people and incredible scientists at the [Human Rights Data Analysis Group](https://hrdag.org/tech-corner/).

My intent is to rediscover the fun I had with my Xanga and MySpace pages 
and explore techniques, skills, and data science related topics I enjoy today. 
Some posts will be more technical, some less so, and many will likely focus on R as
that has been my primary language but you may also find sprinkles of Python, 
SQL, and even SAS as the mood strikes.

Now to add a visitor counter and music...

Thanks for reading!

<!--------------- appendices go here ----------------->

```{r, echo=FALSE}
source("appendix.R")
insert_appendix(
  repo_spec = "jessmhoehner/jblog", 
  name = long_slug
)
```